---
title: "Automated Machine Learning with H2O"
author: "Philip Suskin"
---

# Libraries

```{r}
library(tidyverse)
library(h2o)

library(readxl)
library(GGally)

library(rsample)
library(recipes)
```

# Challenge 1

# Data preparation

```{r}
employee_attrition_tbl <- read_csv("../../HR-Employee-Attrition.csv")

plot_ggpairs <- function(data, color = NULL, density_alpha = 0.5) {
    
    color_expr <- enquo(color)
    
    if (rlang::quo_is_null(color_expr)) {
        
        g <- data %>%
            ggpairs(lower = "blank") 
        
    } else {
        
        color_name <- quo_name(color_expr)
        
        g <- data %>%
            ggpairs(mapping = aes_string(color = color_name), 
                    lower = "blank", legend = 1,
                    diag = list(continuous = wrap("densityDiag", 
                                                  alpha = density_alpha))) +
            theme(legend.position = "bottom")
    }
    
    return(g)
    
}
```

```{r}
# Explore Features by Category

#   1. Descriptive features: age, gender, marital status 
employee_attrition_tbl %>%
    select(Attrition, Age, Gender, MaritalStatus, NumCompaniesWorked, Over18, DistanceFromHome) %>%
    plot_ggpairs(Attrition)

#   2. Employment features: department, job role, job level
employee_attrition_tbl %>%
    select(Attrition, contains("employee"), contains("department"), contains("job")) %>%
    plot_ggpairs(Attrition) 

#   3. Compensation features: HourlyRate, MonthlyIncome, StockOptionLevel 
employee_attrition_tbl %>%
    select(Attrition, contains("income"), contains("rate"), contains("salary"), contains("stock")) %>%
    plot_ggpairs(Attrition)

#   4. Survey Results: Satisfaction level, WorkLifeBalance 
employee_attrition_tbl %>%
    select(Attrition, contains("satisfaction"), contains("life")) %>%
    plot_ggpairs(Attrition)

#   5. Performance Data: Job Involvment, Performance Rating
employee_attrition_tbl %>%
    select(Attrition, contains("performance"), contains("involvement")) %>%
    plot_ggpairs(Attrition)

#   6. Work-Life Features 
employee_attrition_tbl %>%
    select(Attrition, contains("overtime"), contains("travel")) %>%
    plot_ggpairs(Attrition)

#   7. Training and Education 
employee_attrition_tbl %>%
    select(Attrition, contains("training"), contains("education")) %>%
    plot_ggpairs(Attrition)

#   8. Time-Based Features: Years at company, years in current role
employee_attrition_tbl %>%
    select(Attrition, contains("years")) %>%
    plot_ggpairs(Attrition)
```

# Analysis

## Q1: What can you deduce about the interaction between Monthly Income and Attrition?
c. Those that are leaving have a lower Monthly Income

## Q2: What can you deduce about the interaction between Percent Salary Hike and Attrition?
d. It's difficult to deduce anything based on the visualization

## Q3: What can you deduce about the interaction between Stock Option Level and Attrition?
b. Those that are staying have a higher stock option level

## Q4: What can you deduce about the interaction between Environment Satisfaction and Attrition?
a. A higher proportion of those leaving have a low environment satisfaction level

## Q5: What can you deduce about the interaction between Work Life Balance and Attrition?
b. Those that are staying have a higher density of 2's and 3's

## Q6: What Can you deduce about the interaction between Job Involvement and Attrition?
a. Those that are leaving have a lower density of 3's and 4's

## Q7: What can you deduce about the interaction between Over Time and Attrition?
a. The proportion of those leaving that are working Over Time are high compared to those that are not leaving

## Q8: What can you deduce about the interaction between Training Times Last Year and Attrition?
b. People that leave tend to have less annual trainings

## Q9: What can you deduce about the interaction between Years At Company and Attrition?
b. People that leave tend to have less working years at the company

## Q10: What can you deduce about the interaction between Years Since Last Promotion and Attrition?
a. Those that are leaving have more years since last promotion than those that are staying

# Challenge 2

# Data preparation

```{r}
product_backorders_tbl <- read_csv("../../product_backorders.csv")

set.seed(1)

split_obj <- rsample::initial_split(product_backorders_tbl, prop = 0.75)

train_readable_tb1 <- training(split_obj)
test_readable_tb1  <- testing(split_obj)

factor_names <- c("went_on_backorder")
recipie <- recipe(went_on_backorder ~ ., data = train_readable_tb1) %>%  
           step_zv(all_predictors()) %>% 
           step_mutate_at(factor_names, fn = as.factor) %>%
           step_center(all_numeric()) %>%
           step_scale(all_numeric()) %>%
           step_dummy(all_nominal(), -all_outcomes()) %>% 
           prep()

training <- bake(recipie, new_data = train_readable_tb1)
testing  <- bake(recipie, new_data = test_readable_tb1)
```

# H2O

```{r}
h2o.init()
split_h2o <- h2o.splitFrame(as.h2o(training), ratios = c(0.75), seed = 1)
train_h2o <- split_h2o[[1]]
valid_h2o <- split_h2o[[2]]
test_h2o  <- as.h2o(testing)

y <- "went_on_backorder"
x <- setdiff(names(train_h2o), y)

h2o_model <- h2o.automl(x = x,
                        y = y,
                        training_frame    = train_h2o,
                        validation_frame  = valid_h2o,
                        leaderboard_frame = test_h2o,
                        max_runtime_secs  = 30,
                        nfolds            = 5)

typeof(h2o_model)
slotNames(h2o_model)
h2o_model@leaderboard 

h2o_model@leader 
pred_tbl <- h2o.predict(h2o_model@leader, newdata = as.h2o(testing)) %>% 
            as_tibble()
```